### 2016-01-18 paper.tex
Discuss power and drag coefficient curves more; resolves #25

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to the tendency of foils to stall
at higher angles of attack at higher $Re$, and the higher angle of attack ranges
seen by the blades at lower $\lambda$. These effects diminish with increasing
$Re$, which is expected as the blade boundary layers transition to turbulence
closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}.

Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
not collapse exactly onto each other. Note that the data collection was limited
at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
the tow carriage drive belt. In contrast to the power coefficient data, the
rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge 0.6
\times 10^6$.

@@

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of lower virtual camber when compared to the strong $Re$-independence
of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

@@

    \label{fig:cp-re-dep}
\end{figure}

>>>>

Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
tip speed ratio in Fig.~\ref{fig:cp-curves}. $C_P$ is shown to increase in
general with $Re$, along with a reduction in the optimal tip speed ratio, due to
the tendency of foils to stall at higher angles of attack at higher $Re$, and
the higher angle of attack ranges seen by the blades at lower $\lambda$. These
effects diminish with increasing $Re$, which is expected as the blade boundary
layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
    Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer as it moves
against the adverse pressure gradient on the suction side of the foil. Note how
at lower tip speed ratios and Reynolds numbers, $C_P$ becomes significantly
negative, which is possible thanks to the speed control of the experimental
setup's servo motor applying negative torque to the rotor.

@@

Mean rotor drag coefficients are plotted versus tip speed ratio in
Fig.~\ref{fig:cd-curves}. These $C_D$ curves show fewer differences compared to
the power coefficient curves, which is most noticeable at low $\lambda$ and low
$Re$. The relative similarity could be attributed to the effects of stall, where
the lift-to-drag ratio on the blades may drop, decreasing rotor torque, though
the total resultant force due to high blade drag retains a similar component in
the streamwise direction.

@@

Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
not collapse exactly onto each other. Note that the data collection was limited
at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
the tow carriage drive belt. However, in contrast to the power coefficient data,
the rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge
0.6 \times 10^6$.

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. We see that the power coefficient of the turbine
increases dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda
U_\infty c / \nu \approx 2 \times 10^5$, beyond which there appears to be a
small, linear, positive trend. The tendency of $C_P$ to continue increasing
slightly could be an effect of lower ``virtual camber''---or flow curvature
\cite{Migliore1980}---when compared to the strong $Re$-independence of the
higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

@@

    \label{fig:perf-re-dep}
\end{figure}
